### 2017-06-28 Elle/Elle.tex
Definition for \eta, \mu, and strength \tau in Elle

\noindent
Deriving exchange in Elle comonadicly:

@@

Deriving weakening in Elle comonadicly:
\begin{center}
  \tiny
  \begin{math}
    $$\mprset{flushleft}
    \inferrule* [right={\tiny impR}] {
      $$\mprset{flushleft}
      \inferrule* [right={\tiny Fl}] {
        $$\mprset{flushleft}
        \inferrule* [right={\tiny weak}] {
          $$\mprset{flushleft}
          \inferrule* [right={\tiny unitR}] {
            \,
          }{[[. |- triv : Unit]]}
        }{[[x0 : Gf A ; . |- weak x0 in triv : Unit]]}
      }{[[x1 : F Gf A ; . |- let x1 : F Gf A be F x0 in weak x0 in triv : Unit]]}
    }{[[. ; . |- \l x1 : F Gf A . let x1 : F Gf A be F x0 in weak x0 in triv : (F Gf A) -> (Unit)]]}
  \end{math}
\end{center}

>>>>

Deriving exchange in Elle comonadicly:

@@

Deriving weakening in Elle comonadicly:
\begin{center}
  \tiny
  \begin{math}
    $$\mprset{flushleft}
    \inferrule* [right={\tiny impR}] {
      $$\mprset{flushleft}
      \inferrule* [right={\tiny Fl}] {
        $$\mprset{flushleft}
        \inferrule* [right={\tiny weak}] {
          $$\mprset{flushleft}
          \inferrule* [right={\tiny unitR}] {
            \,
          }{[[. |- triv : Unit]]}
        }{[[x0 : Gf A ; . |- weak x0 in triv : Unit]]}
      }{[[. ; x1 : F Gf A |- let x1 : F Gf A be F x0 in weak x0 in triv : Unit]]}
    }{[[. ; . |- \l x1 : F Gf A . let x1 : F Gf A be F x0 in weak x0 in triv : (F Gf A) -> (Unit)]]}
  \end{math}
\end{center}

$GF$ is a monad:
\begin{itemize}
\item Deriving $\eta$:
  \begin{center}
    \tiny
    \begin{math}
      $$\mprset{flushleft}
      \inferrule* [right={\tiny impR}] {
        $$\mprset{flushleft}
        \inferrule* [right={\tiny Gr}] {
          $$\mprset{flushleft}
          \inferrule* [right={\tiny Gl}] {
            $$\mprset{flushleft}
            \inferrule* [right={\tiny Fl}] {
              $$\mprset{flushleft}
              \inferrule* [right={\tiny Gl}] {
                $$\mprset{flushleft}
                \inferrule* [right={\tiny ax}] {
                  \,
                }{[[. ; x0 : F X |- x0 : F X]]}
              }{[[x1 : Gf F X ; . |- let x1 : Gf F X be Gf x0 in x0 : F X]]}
            }{[[. ; x2 : F Gf F X |- let x2 : F Gf F X be F x1 in (let x1 : Gf F X be Gf x0 in x0) : F X]]}
          }{[[x3 : Gf F Gf F X ; . |- let x3 : Gf F Gf F X be Gf x2 in (let x2 : F Gf F X be F x1 in (let x1 : Gf F X be Gf x0 in x0)) : F X]]}
        }{[[x3 : Gf F Gf F X |- Gf (let x3 : Gf F Gf F X be Gf x2 in (let x2 : F Gf F X be F x1 in (let x1 : Gf F X be Gf x0 in x0))) : Gf F X]]}
      }{[[ . |- \l x3 : Gf F Gf F X . Gf (let x3 : Gf F Gf F X be Gf x2 in (let x2 : F Gf F X be F x1 in (let x1 : Gf F X be Gf x0 in x0))) : (Gf F Gf F X) -> (Gf F X)]]}
    \end{math}
  \end{center}
\item Deriving $\mu$:
  \begin{center}
    \tiny
    \begin{math}
      $$\mprset{flushleft}
      \inferrule* [right={\tiny impR}] {
        $$\mprset{flushleft}
        \inferrule* [right={\tiny Gr}] {
          $$\mprset{flushleft}
          \inferrule* [right={\tiny Fr}] {
            $$\mprset{flushleft}
            \inferrule* [right={\tiny ax}] {
              \,
            }{[[x : X |- x : X]]}
          }{[[x : X ; . |- F x : F X]]} 
        }{[[x : X |- Gf F x : Gf F X]]}
      }{[[. |- \l x : X . Gf F x : (X) -> (Gf F X)]]}
    \end{math}
  \end{center}
\end{itemize}

The monad $GF$ is strong:
\begin{itemize}
\item Deriving the tensorial strength $\tau$:
  \begin{center}
    \tiny
    \begin{math}
      $$\mprset{flushleft}
      \inferrule* [right={\tiny impR}] {
        $$\mprset{flushleft}
        \inferrule* [right={\tiny tenL}] {
          $$\mprset{flushleft}
          \inferrule* [right={\tiny beta}] {
            $$\mprset{flushleft}
            \inferrule* [right={\tiny Gr}] {
              $$\mprset{flushleft}
              \inferrule* [right={\tiny Gl}] {
                $$\mprset{flushleft}
                \inferrule* [right={\tiny Fl}] {
                  $$\mprset{flushleft}
                  \inferrule* [right={\tiny Fr}] {
                    $$\mprset{flushleft}
                    \inferrule* [right={\tiny tenR}] {
                      $$\mprset{flushleft}
                      \inferrule* [right={\tiny ax}] {
                        \,
                      }{[[x0 : X |- x0 : X]]}
                      $$\mprset{flushleft}
                      \inferrule* [right={\tiny ax}] {
                        \,
                      }{[[y0 : Y |- y0 : Y]]}
                    }{[[x0 : X , y0 : Y |- x0 (x) y0 : h(X) (x) Y]]}
                  }{[[x0 : X , y0 : Y ; . |- F (x0 (x) y0) : F (h(X) (x) Y)]]}
                }{[[x0 : X ; y1 : F Y |- let y1 : F Y be F y0 in F (x0 (x) y0) : F (h(X) (x) Y)]]}
              }{[[y2 : Gf F Y , x0 : X ; . |- let y2 : Gf F Y be Gf y1 in (let y1 : F Y be F y0 in F (x0 (x) y0)) : F (h(X) (x) Y)]]}
            }{[[y2 : Gf F Y , x0 : X |- Gf (let y2 : Gf F Y be Gf y1 in (let y1 : F Y be F y0 in F (x0 (x) y0))) : Gf F (h(X) (x) Y)]]}
          }{[[x1 : X , y3 : Gf F Y |- ex y3 , x1 with y2 , x0 in (Gf (let y2 : Gf F Y be Gf y1 in (let y1 : F Y be F y0 in F (x0 (x) y0)))) : Gf F (h(X) (x) Y)]]}
        }{[[z : h(X) (x) Gf F Y |- let z : h(X) (x) Gf F Y be x1 (x) y3 in (ex y3 , x1 with y2 , x0 in (Gf (let y2 : Gf F Y be Gf y1 in (let y1 : F Y be F y0 in F (x0 (x) y0))))) : Gf F (h(X) (x) Y)]]}
      }{[[. |- \l z : h(X) (x) Gf F Y . let z : h(X) (x) Gf F Y be x1 (x) y3 in (ex y3 , x1 with y2 , x0 in (Gf (let y2 : Gf F Y be Gf y1 in (let y1 : F Y be F y0 in F (x0 (x) y0))))) : (h(X) (x) Gf F Y) -> (Gf F (h(X) (x) Y))]]}
    \end{math}
  \end{center}
\end{itemize}
